---
name: An Shu Te
position: "Masters Student (Clinical Psychology)"
address: |
         | National University of Singapore
profilepic: 
phone: +65 9877 0811
email: "teanshu97@gmail.com"
twitter: anshu_te97
github: anshu-97
linkedin: an-shu-te-101238201
researchgate: An-Shu-Te
orcid: 0000-0001-8008-2824
headcolor: 009ACD
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: false
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{dark-gray}{gray}{1.5}
  \colorlet{text}{darkgray}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(ggplot2)
library(dplyr)
library(sf)
library(rnaturalearth)
library(sfnetworks)
library(ggrepel)
library(emojifont)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(gridExtra)
```



<!-- | Nationality: Ecuadorian, Birthdate: 05/01/1994 -->

Biography
==========================================

\paragraphstyle{My research interests lie in emotion regulation, particularly in investigating its association with interoception and maladaptive personality traits. I am also interested in investigating the mechanistic underpinnings of psychotic and mood disorders, as well as the role of parent-child attachments on children's externalizing and interalizing behaviours.}

\faIcon{briefcase} Research Experience
============================================

```{r research, eval = T}

tibble:: tribble(
  ~title, ~date, ~company, ~location, ~desc,
  'Research Assistant', '10-2021, 08-2023', 'Clinical Brain Lab', 'Nanyang Technological University', c(
    'Develop and conduct online cognitive behavioural tasks and surveys (using jsPscyh etc.,)',
    'Perform EEG, physiological and behavioural data collection, preprocessing and data analysis',
    'Coordinate data collection and cognitive training sessions.',
    'Assist in the preparation and writing of progress reports, scientific presentations, manuscripts, abstracts and publications',
    'Manage and maintain project records.',
    'Coordinate project meetings and facilitate communication among project personnel',
    'Develop and maintain project operational procedures, training materials and documents',
     'Train and mentor other research assistants and student assistants'),
  'Research Assistant', '05-2021, 10-2021', 'ABC Lab', 'Singapore Management University', c('Recruit subjects on and off campus',
    'Develop and conduct surveys and cognitive behavioural tasks',
    'Summarize research findings and preprocess data',
    'Assisting in the preparation and writing of progress reports, scientific presentations, abstracts, manuscripts and publications',
    'Train and mentor other research assistants and student assistants')
) |> 
  detailed_entries(what=title, when=date, with=company, where=location, why=desc, .protect = TRUE)

```


\faIcon{chalkboard} Clinical/Teaching Experience
==================================================

```{r teaching, eval = T}
tibble:: tribble(
  ~title, ~date, ~company, ~location, ~desc,
  'Research Assistant', '08-2022, 08-2022', 'Clinical Brain Lab', 'Nanyang Technological University', c('Conducted an "Intro to Github" workshop'),
  'Research Assistant', '05-2021, 10-2021', 'ABC Lab', 'Singapore Management University', c('Screen older adults for neurocognitive deficits using assessment tools'),
  'Special Education Teacher', '08-2020, 05-2021', 'Fernvale Garden School', 'Movement for the Intellectually Disabled', c('Taught students (7 - 18 year olds) with moderate to severe neurodevelopmental and behavioural disorders a range of subjects (English, Math etc.,) as well as basic living skills','Teach students different coping mechanisms to manage behavioural disorders and facilitate behaviour management workshops','Provide regular assessment of living skills, educational progress and behavioural management for children', 'Formulate individualized education plans and treatment and inetervention plans regularly', "Provide basic assessment of children's behavioural needs as well as educational progress",'Support students’ learning using a range of different teaching strategies and handmade as well as self-sourced IT resources'),'Intern', '06-2019, 08-2019', 'Childrens Partnership Pte Ltd', 'Singapore', c('Shadow principal psychologist and assist during intervention sessions','Provide brief case reports based on clinical observations', 'Engage and teach children in special needs teaching programmes', 'Organize social and special needs educational programs to facilitate learning for children', 'Facilitate social skills training and behavioural interventions')
) |> 
  detailed_entries(what=title, when=date, with=company, where=location, why=desc, .protect=TRUE)
```



\faIcon{university} Education
==================================

```{r education, eval = T}
tibble:: tribble(
  ~ study, ~ university, ~ loc, ~ dates, ~ details,
    "Department of Psychology", "National University of Singapore", "Singapore", "2016 - 2020", c("Bachelor of Social Sciences with Honors (Highest Distinction) in Psychology", "Honors Thesis: What Happens After we Choose to Eat the Forbidden Fruit - Effects of Indulgence Autonomy on Post-Temptation Motivation"),)|> 
  detailed_entries(study, dates, university, loc, details, .protect=TRUE)
```

\faIcon*{file} Publications
===========================

\footnotesize
- Makowski D, Lau ZJ, Pham T, **Te, A.**, et al. (2023, 23 April) The Heart can Lie: The Role of Interoception and Theory of Mind in Deception. (under review). DOI: 10.31234/osf.io/p342w.
- Mavros, P., Ngoi, Z., Kirk, S., **Te, A.**, et al. (2023, May 15). Attenuating subjective crowding through beauty: an online study on the interaction between environment aesthetics, typology and crowdedness. (under review). DOI: https://doi.org/10.31234/osf.io/ezybm
- Makowski, D., **Te, A.**, Kirk, S., Liang, N. Z., & Chen, S. A. The Illusion Game: A Novel Experimental Paradigm Provides Evidence for a General Factor of Visual Illusion Sensitivity and Personality Correlates. *Scientific Reports* (2023). https://doi.org/10.31234/osf.io/9pjx5
- Yang, H., Tng, G.Y.Q., Khoo, S.S. & **Te, A.** Smartphone-use profiles and cognitive and socioemotional outcomes in middle-aged and older adults: a latent profile analysis. *Curr Psychol* (2023). https://doi.org/10.1007/s12144-023-04537-w 
- Makowski, D., **Te, A.**, Pham, T., Lau, Z., & Chen, S. A. The Structure of Chaos: An Empirical Comparison of Fractal Physiology Complexity Indices using NeuroKit2. *Entropy* (2022).  https://doi.org/10.3390/e24081036

\normalsize

<!--
\faIcon{lightbulb} Projects
=====================================

\smallskip

\faIcon{satellite} Research projects
---------------------------------
\par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} 


```{r proj}
proj <- tibble:: tribble(
  ~ name, ~ acronym, ~ date, ~study_area, 
  "A Neuroscientific Investigation of the Interaction between Crowdedness and Environment Typology", "NICE", "2021 - 2022", "SG", 
  "That's Fake News: Modulating the Neurocognitive Processes Underlying the Belief in Deceptive Information", "PPF", "2021-2022", "SG",
  "Cognitive, Neural and Social Factors involved in the Perception of Real vs Fake Information", "PROOF", "2022-2025", "SG",)
  
proj <- proj|> 
  detailed_entries(with = acronym, what = name, when = date, where = study_area, .protect=TRUE)  
```


<!--
\faIcon{laptop-code} Programming projects
----------------------------------
<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

<!--
```{r dev}
tribble(
  ~ name, ~ sum, ~ acronym, ~ type, ~ lang, ~ link,
  "Landslide dammed-lakes detection and monitoring after the Kaikōura earthquake in New Zealand", 
  "GEE project: Landslide dammed-lakes detection and monitoring in Kaikōura, NZ",
  "Kaikoura landslide dammed-lakes \\href{https://github.com/loreabad6/KaikouraDammedLakes_public}{\\tiny{\\faLink}}", 
  "GEE project",
  "JavaScript",
  "\\href{https://github.com/loreabad6/KaikouraDammedLakes_public}{\\faGithub}",
  
  "Blog: Lore Abad", 
  "Lore Abad: Distill blog with my data science work", 
  "Blog \\href{https://loreabad6.github.io/}{\\tiny{\\faLink}}", 
  "Distill blog",
  "R",
  "\\href{https://loreabad6.github.io/}{\\faGlobe}",
  
  "Tidy Geospatial Networks in R", 
  "\\textit{sfnetworks} Tidy Geospatial Networks in R", 
  "sfnetworks \\href{https://luukvdmeer.github.io/sfnetworks/}{\\tiny{\\faLink}}", 
  "R Package",
  "R",
  "\\href{https://luukvdmeer.github.io/sfnetworks/}{\\faGithub}",
  
  "Bicycle Network Analysis Score for UK and NL",
  "BNA-EU: Bicycle Network Analysis Score for UK and NL",
  "BNA-EU \\href{https://github.com/loreabad6/masters-thesis-geotech}{\\tiny{\\faLink}}", 
  "RMarkdown Reporting",
  "R \\& SQL",
  "\\href{https://github.com/loreabad6/masters-thesis-geotech}{\\faGithub}"
) |> 
  brief_entries(with = lang, what = sum, when = link, .protect=FALSE)  
```
-->


\faIcon{comments} Conferences & Presentations
================================

```{r conferences}
tibble:: tribble(
  ~ title, ~ event, ~ date,
  "EEG Complexity as a Marker of Spontaneous Lies", "Organization for Human Brain Mapping (OHBM)", "07, 2023",
  "Neurokit2: An open-source Python software to analyse physiological data", "Organization for Human Brain Mapping (OHBM)", "07, 2023",
  "Fractal dimension of EEG activity is linked to distinct facets of resting-state cognition",  "Organization for Human Brain Mapping (OHBM)", "06, 2022",
  "A Closer Look at Cardiac Contraction and the Effect of Cardiac Timing on Cognitive Control",  "Organization for Human Brain Mapping (OHBM)", "06, 2022",
)|> 
  detailed_entries(with = title, where = event, when = date, .protect=TRUE)  
```


\faIcon{medal} Awards & Distinctions
===============================

```{r dist}
tibble:: tribble(
  ~ area, ~ org, ~ date,
    "Deans List", "National University of Singapore", "2020",
  "Wan Boo Sow Chinese Studies (GE)", "National University of Singapore", "2019",
  "Deans List", "National University of Singapore", "2019",
)|> 
  brief_entries(what = area, when = date, with = org, .protect=TRUE)
```

\faIcon{hand-holding-heart} Volunteer work
===============================

```{r vol}
tibble:: tribble(
  ~ desc, ~location, ~ date,
  "Regular volunteer (IMHope)", "Institute of Mental Health", "2022-Current",
  "Regular Volunteer", "Singapore After-Care Association", "2022-Current",
  "Overseas volunteer (Project Sangkhem)", "Cambodia", "2019",
  "Intern", "Children's Partnership Pte Ltd (Singapore)", "2019"
)|> 
  brief_entries(what = desc, with=location, when = date, .protect=TRUE)
```

<!-- 
\faIcon{users} Memberships
===============================
```{r org}
tribble(
  ~ org, ~ date,
  "R-Ladies Global \\href{https://rladies.org/austria-rladies/name/lorena-abad/}{\\tiny{\\faIcon{link}}}", "since 2020",
  "Women in Geospatial \\href{https://speakers.womeningeospatial.org/speakers}{\\tiny{\\faIcon{link}}}", "since 2020",
  "European Geosciences Union", "since 2020",
  "Erasmus Mundus Association", "since 2020"
) |> 
  brief_entries(what = org, when = date, .protect = F)
```
-->

\faIcon{brain} Skills
================================

\smallskip

\faIcon{cogs} Technical skills
---------------------------------
<!-- \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}} -->

<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

```{r techtable, results='markup'}
tribble(
   ~`Coding Languages`, ~Software, ~Other,
  "R -- Python -- SPSS",
  "RStudio -- jsPsych -- PsychoPy",
  "Git -- Markdown"
) |>
  knitr::kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kableExtra::kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  kableExtra::row_spec(0, bold = T, color = "#009acd") |> 
  kableExtra::row_spec(1, bold = F, color = "#7f7f7f") |> 
  kableExtra::column_spec(column = 1:3, width = '4.75cm')
```

<!-- \smallskip -->

<!--
\faIcon{calendar} Organizational skills
------------------------------
```{r events}
tribble(
  ~ event, ~ date, ~ place,
  "e-Rum 2020 satellite event: \\textit{sfnetworks} Webinar and Hackathon \\href{https://2020.erum.io/program/hackathon/}{\\tiny{\\faIcon{link}}}", "06, 2020", "Online Event",
  "citizenMorph App Testing Workshop", "09, 2019", "Höfn, IS",
  "GeoMundus 2018 \\href{http://www.geomundus.org/2018/}{\\tiny{\\faIcon{link}}}", "12, 2018", "Lisbon, PT",
  # "I University Simposium of Environmental Science Research", "06, 2016", "Cuenca, EC",
  "Vicepresident of the Student Association of Environmental Engineers", "2013 - 2014", "Cuenca, EC",
) |> 
  brief_entries(what = event, when = date, with = place, .protect = F)
```
  -->
  
\smallskip

\faIcon{language} Languages
-------------------------------

```{r langforeign, results='markup'}
data.frame(
  Skill = c("Reading", "Writing", "Listening","Speaking"),
  English = kableExtra::cell_spec(c("Native", "Native", "Native", "Native"), "latex", color="#009acd"),
  Mandarin=kableExtra::cell_spec(c("Native", "Native", "Native", "Native"), "latex", color="#4cb8dc") ) |>
  knitr::kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kableExtra::kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  kableExtra::column_spec(column = 1:6, width = '2.4cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

\faIcon{comment} References
=============================

\footnotesize

- **Prof. Dr. Annabel Chen**, Nanyang Technological University, NTU, annabelchen@ntu.edu.sg 
- **Dr. Dominique Makowski** Nanyang Technological University, NTU, dom.makowski@gmail.com


\normalsize

<!-- \footnotesize -->
<!-- \begin{multicols}{3} -->
<!-- \begin{center} -->

<!-- \textbf{Prof. Dr. Edzer Pebesma} \newline -->
<!-- \faIcon{phone} +49 251 83-33081 \newline -->
<!-- \faIcon{at} edzer.pebesma@uni-muenster.de \newline -->
<!-- \faIcon{envelope} Institute for Geoinformatics \newline -->
<!-- Heisenbergstraße 2, \newline -->
<!-- 48149 Münster, Germany -->

<!-- \textbf{Prof. Dr. Marco Painho} \newline -->
<!-- \faIcon{phone} +351 213 871 573 \newline -->
<!-- \faIcon{at} painho@novaims.unl.pt \newline -->
<!-- \faIcon{envelope} NOVA Information Management School \newline -->
<!-- Campus de Campolide\newline -->
<!-- 1070-312 Lisbon, Portugal -->

<!-- \textbf{Mag. Daniel Hölbling} \newline -->
<!-- \faIcon{phone} +43 (0)662 8044 7581 \newline -->
<!-- \faIcon{at} daniel.hoelbling@plus.ac.at \newline -->
<!-- \faIcon{envelope} Department of Geoinformatics - Z\_GIS 'newline -->
<!-- Schillerstrasse 30 \newline -->
<!-- 5020 Salzburg, Austria -->
<!-- \end{center} -->
<!-- \end{multicols} -->

<!-- \normalsize -->
