---
name: An Shu Te
position: "Masters Student (Clinical Psychology)"
address: |
         | National University of Singapore
profilepic: 
#phone: +65 9877 0811
email: "anshu.te@nus.edu.sg"
twitter: anshu_te97
github: anshu-97
linkedin: an-shu-te-101238201
researchgate: An-Shu-Te
orcid: 0000-0001-8008-2824
headcolor: 009ACD
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: false
    show_footer: true
    includes:
      in_header: header.txt
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(ggplot2)
library(dplyr)
library(sf)
library(rnaturalearth)
library(sfnetworks)
library(ggrepel)
library(emojifont)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(gridExtra)
```



<!-- | Nationality: Ecuadorian, Birthdate: 05/01/1994 -->

Biography
==========================================

\paragraphstyle{My research interests lie in emotion regulation, particularly in its association with interoception and personality traits. I am also interested in investigating the underpinnings of psychotic and mood disorders, as well as the role of parent-child attachments on children's behaviours.}


\faIcon{hospital} Clinical Experience
==================================================

```{r clinical, eval = T}
tibble:: tribble(
  ~title, ~date, ~company, ~location, ~desc,
  'Paediatrics Psychological Services', '01-2025, 06-2025', 'Clinical Psychologist-in-Training', 'National Univeristy Hospital', c('Implemented appropriate psychotherapy interventions for inpatients and outpatients between 6 to 18 years old', 'Conducted psychometric assessments for referred patients', 'Worked with a multidisciplinary team and contributed to the overall care plan of patients', 'Assisted in the development of materials for patients'),
  
  'Hougang Sheng Hong Family Service Centre/ Kampong Kapor Community Services', '07-2024, 12-2024', 'Clinical Psychologist-in-Training', 'Community Psychology Hub', c('Conducted appropriate psychotherapy interventions and trauma assessments for adults and children', 'Conducted psychometric and mental health assessments for vulnerable adults and preschool children', 'Worked with a multidisciplinary team and contributed to the overall care plan of clients', 'Conducted a workshop for female survivors of family violence'),
  
  'Clinical and Health Psychology Centre', '01-2024, 06-2024', 'Clinical Psychologist-in-Training', 'National University of Singapore', c('Implemented appropriate psychotherapy interventions for adults and youths', 'Conducted psychometric assessments for adults and children'),
  
  'Childrens Partnership Pte Ltd', '06-2019, 08-2019', 'Psychology Intern', 'Childrens Partneship Pte Ltd (Singapore)', c('Shadowed principal psychologist and assisted in psychotherapy interventions','Wrote brief case reports based on clinical observations', 'Engaged and taught children in special needs teaching programmes', 'Co-facilitated social skills training and behavioural intervention sessions'),
  
) |> 
  detailed_entries(what=title, when=date, with=company, where=location, why=desc, .protect=TRUE)
```

\faIcon{briefcase} Research Experience
============================================

```{r research, eval = T}

tibble:: tribble(
  ~title, ~date, ~company, ~location, ~desc,
  'Clinical Brain Lab', '10-2021, 08-2023', 'Research Assistant', 'Nanyang Technological University', c(
    'Developed and conducted online cognitive tasks and surveys (using jsPscyh, Python etc.,)',
    'Assisted in the collection of EEG, physiological and behavioural data', 
    'Performed preprocessing and data analysis',
    'Assisted in the preparation and writing of scientific presentations, manuscripts, abstracts and publications',
     'Trained and mentored research and student assistants'),
  
  'ABC Lab', '05-2021, 10-2021', 'Research Assistant', 'Singapore Management University', c('Developed and conducted online surveys and cognitive tasks with older adults and preschool children',
    'Assisted in the screening of older adults for neurocognitive deficits using psychometric assessment tools',
    'Performed preprocessing of collected data',
    'Assisted in the preparation and writing of scientific presentations, abstracts, manuscripts and publications',
    'Trained and mentored research and student assistants')
) |> 
  detailed_entries(what=title, when=date, with=company, where=location, why=desc, .protect = TRUE)

```

\faIcon{chalkboard} Other Experience
==================================================

```{r teaching, eval = T}
tibble:: tribble(
  ~title, ~date, ~company, ~location, ~desc,
 'Fernvale Garden School', '08-2020, 05-2021', 'Special Education Teacher', 'Movement for the Intellectually Disabled (MINDS)', c('Taught 7 - 18 year olds with moderate to severe neurodevelopmental disorders academic subjects and daily living skills','Co-facilitated behaviour management workshops for students', 'Conceptualised individualized education plans and intervention plans for students', "Conducted basic assessments of students' behavioural needs as well as educational progress")
) |> 
  detailed_entries(what=title, when=date, with=company, where=location, why=desc, .protect=TRUE)
```


\faIcon{university} Education
==================================

```{r education, eval = T}
tibble:: tribble(
  ~ study, ~ university, ~ loc, ~ dates, ~details,
  "National University of Singapore", "Master of Psychology (Clinical)", "Singapore", "2023 - 2025", c("Master's Dissertation: Exploring Latent Profiles in Informant Discrepancies: A Study of Youth Behaviour in Singapore"),
    "National University of Singapore", "Bachelor of Social Sciences (Honors) in Psychology", "Singapore", "2016 - 2020", c("Graduated with Highest Distinction: 4.80/5.0","Honors Thesis: What Happens After we Choose to Eat the Forbidden Fruit - Effects of Indulgence Autonomy on Post-Temptation Motivation"),
 "University of Toronto (St. George Campus)", "University Exchange Programme", "Canada", "2018", c("NASA Exchange Scholarship"))|> 
  detailed_entries(study, dates, university, loc, details, .protect=TRUE)
```

\faIcon*{file} Publications 
===============================

\footnotesize
- Makowski D., **Te, A.**, Neves, A., Kirk, S., Ngoi., Mavros., Chen, S.A. Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Articifically Generated. *Acta Psychologica* (2025). https://doi.org/10.1016/j.actpsy.2024.104670
- Makowski D., Lau, Z.J., Pham, T., **Te, A.**, Kirk, S., Liauw, C., Chen, S.A. The Heart can Lie: A Preliminary Investigation of the Role of Interoception and Theory of Mind in Deception. *Current Psychology* (2024). https://doi.org/10.1007/s12144-024-06890-w
- Makowski, D., **Te, A.**, Kirk, S., Liang, N. Z., & Chen, S. A. The Illusion Game: A Novel Experimental Paradigm Provides Evidence for a General Factor of Visual Illusion Sensitivity and Personality Correlates. *Scientific Reports* (2023). https://doi.org/10.31234/osf.io/9pjx5
- Yang, H., Tng, G.Y.Q., Khoo, S.S. & **Te, A.** Smartphone-use profiles and cognitive and socioemotional outcomes in middle-aged and older adults: a latent profile analysis. *Current Psychology* (2023). https://doi.org/10.1007/s12144-023-04537-w 
- Makowski, D., **Te, A.**, Pham, T., Lau, Z., & Chen, S. A. The Structure of Chaos: An Empirical Comparison of Fractal Physiology Complexity Indices using NeuroKit2. *Entropy* (2022).  https://doi.org/10.3390/e24081036
- Mavros, P., Ngoi, Z., Kirk, S., **Te, A.**, et al. (2023, May 15). Attenuating subjective crowding through beauty: an online study on the interaction between environment aesthetics, typology and crowdedness. (under review). DOI: https://doi.org/10.31234/osf.io/ezybm

\normalsize

<!--
\faIcon{lightbulb} Projects
=====================================

\smallskip

\faIcon{satellite} Research projects
---------------------------------
\par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} 


```{r proj}
proj <- tibble:: tribble(
  ~ name, ~ acronym, ~ date, ~study_area, 
  "A Neuroscientific Investigation of the Interaction between Crowdedness and Environment Typology", "NICE", "2021 - 2022", "SG", 
  "That's Fake News: Modulating the Neurocognitive Processes Underlying the Belief in Deceptive Information", "PPF", "2021-2022", "SG",
  "Cognitive, Neural and Social Factors involved in the Perception of Real vs Fake Information", "PROOF", "2022-2025", "SG",)
  
proj <- proj|> 
  detailed_entries(with = acronym, what = name, when = date, where = study_area, .protect=TRUE)  
```


<!--
\faIcon{laptop-code} Programming projects
----------------------------------
<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

<!--
```{r dev}
tribble(
  ~ name, ~ sum, ~ acronym, ~ type, ~ lang, ~ link,
  "Landslide dammed-lakes detection and monitoring after the Kaikōura earthquake in New Zealand", 
  "GEE project: Landslide dammed-lakes detection and monitoring in Kaikōura, NZ",
  "Kaikoura landslide dammed-lakes \\href{https://github.com/loreabad6/KaikouraDammedLakes_public}{\\tiny{\\faLink}}", 
  "GEE project",
  "JavaScript",
  "\\href{https://github.com/loreabad6/KaikouraDammedLakes_public}{\\faGithub}",
  
  "Blog: Lore Abad", 
  "Lore Abad: Distill blog with my data science work", 
  "Blog \\href{https://loreabad6.github.io/}{\\tiny{\\faLink}}", 
  "Distill blog",
  "R",
  "\\href{https://loreabad6.github.io/}{\\faGlobe}",
  
  "Tidy Geospatial Networks in R", 
  "\\textit{sfnetworks} Tidy Geospatial Networks in R", 
  "sfnetworks \\href{https://luukvdmeer.github.io/sfnetworks/}{\\tiny{\\faLink}}", 
  "R Package",
  "R",
  "\\href{https://luukvdmeer.github.io/sfnetworks/}{\\faGithub}",
  
  "Bicycle Network Analysis Score for UK and NL",
  "BNA-EU: Bicycle Network Analysis Score for UK and NL",
  "BNA-EU \\href{https://github.com/loreabad6/masters-thesis-geotech}{\\tiny{\\faLink}}", 
  "RMarkdown Reporting",
  "R \\& SQL",
  "\\href{https://github.com/loreabad6/masters-thesis-geotech}{\\faGithub}"
) |> 
  brief_entries(with = lang, what = sum, when = link, .protect=FALSE)  
```
-->


\faIcon{comments} Conferences & Presentations
================================

```{r conferences}
tibble:: tribble(
  ~ title, ~ event, ~ date,
  "EEG Complexity as a Marker of Spontaneous Lies", "Organization for Human Brain Mapping (OHBM)", "07, 2023",
  "Neurokit2: An open-source Python software to analyse physiological data", "Organization for Human Brain Mapping (OHBM)", "07, 2023",
  "Fractal dimension of EEG activity is linked to distinct facets of resting-state cognition",  "Organization for Human Brain Mapping (OHBM)", "06, 2022",
  "A Closer Look at Cardiac Contraction and the Effect of Cardiac Timing on Cognitive Control",  "Organization for Human Brain Mapping (OHBM)", "06, 2022",
)|> 
  detailed_entries(with = title, where = event, when = date, .protect=TRUE)  
```

\faIcon{medal} Awards & Distinctions
===============================

```{r dist}
tibble:: tribble(
  ~ area, ~ org, ~ date,
  "NCSS Social Service Scholarship","National Council of Social Service", "2023",
    "Deans List", "National University of Singapore", "2020",
  "Wan Boo Sow Chinese Studies (GE)", "National University of Singapore", "2019",
  "Deans List", "National University of Singapore", "2019",
)|> 
  brief_entries(what = area, when = date, with = org, .protect=TRUE)
```

\faIcon{hand-holding-heart} Volunteering Experience
===============================

```{r vol}
tibble:: tribble(
  ~ desc, ~location, ~ date,
  "IMHope", "Institute of Mental Health", "2022-Current",
  "Volunteer After-Care Programme", "Singapore After-Care Association", "2022-Current",
  "Project Sangkhem (overseas volunteer)", "Cambodia", "2019",
)|> 
  brief_entries(what = desc, with=location, when = date, .protect=TRUE)
```

<!-- 
\faIcon{users} Memberships
===============================
```{r org}
tribble(
  ~ org, ~ date,
  "R-Ladies Global \\href{https://rladies.org/austria-rladies/name/lorena-abad/}{\\tiny{\\faIcon{link}}}", "since 2020",
  "Women in Geospatial \\href{https://speakers.womeningeospatial.org/speakers}{\\tiny{\\faIcon{link}}}", "since 2020",
  "European Geosciences Union", "since 2020",
  "Erasmus Mundus Association", "since 2020"
) |> 
  brief_entries(what = org, when = date, .protect = F)
```
-->

\faIcon{brain} Skills
================================

\smallskip

<!-- \smallskip -->

<!--
\faIcon{calendar} Organizational skills
------------------------------
```{r events}
tribble(
  ~ event, ~ date, ~ place,
  "e-Rum 2020 satellite event: \\textit{sfnetworks} Webinar and Hackathon \\href{https://2020.erum.io/program/hackathon/}{\\tiny{\\faIcon{link}}}", "06, 2020", "Online Event",
  "citizenMorph App Testing Workshop", "09, 2019", "Höfn, IS",
  "GeoMundus 2018 \\href{http://www.geomundus.org/2018/}{\\tiny{\\faIcon{link}}}", "12, 2018", "Lisbon, PT",
  # "I University Simposium of Environmental Science Research", "06, 2016", "Cuenca, EC",
  "Vicepresident of the Student Association of Environmental Engineers", "2013 - 2014", "Cuenca, EC",
) |> 
  brief_entries(what = event, when = date, with = place, .protect = F)
```
  -->

\faIcon{language} Languages
-------------------------------
\footnotesize
- **English (Native)**
- **Mandarin (Proficient)**
\normalsize
\smallskip
<!--
```{r langforeign, results='markup'}
data.frame(
  Language = c("English", "Mandarin"),
  Proficiency = kableExtra::cell_spec(c("Native", "Proficient"), "latex", color="#009acd"))|>
  # Mandarin=kableExtra::cell_spec(c("Proficient", "Proficient", "Native", "Proficient"), "latex", color="#4cb8dc") ) |>
  knitr::kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kableExtra::kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  kableExtra::column_spec(column = 1:6, width = '2cm') #|> 
  # add_header_above(' ', line = F) |>
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```
-->
\smallskip

\faIcon{cogs} Technical skills
---------------------------------
<!-- \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}} -->

<!-- \par\noindent\nobreak\vspace{-30pt}\rule{\textwidth}{1pt} -->

```{r techtable, results='markup'}
tribble(
   ~`Coding Languages`, ~Software, ~Other,
  "R -- Python -- SPSS",
  "jsPsych -- PsychoPy",
  "Git -- Markdown"
) |>
  knitr::kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kableExtra::kable_styling(full_width = F, font_size = 9, latex_options = "HOLD_position") |> 
  kableExtra::row_spec(0, bold = T, color = "#009acd") |> 
  kableExtra::row_spec(1, bold = F, color = "#7f7f7f") |> 
  kableExtra::column_spec(column = 1:3, width = '4.75cm')
```

<!-- \faIcon{comment} References -->
<!-- ============================= -->

<!-- \footnotesize -->

<!-- - **Prof. Dr. Annabel Chen**, Nanyang Technological University, Singapore, annabelchen@ntu.edu.sg  -->
<!-- - **Dr. Dominique Makowski**, University of Sussex, United Kingdom, dom.makowski@gmail.com -->


<!-- \normalsize -->

<!-- \footnotesize -->
<!-- \begin{multicols}{3} -->
<!-- \begin{center} -->

<!-- \textbf{Prof. Dr. Edzer Pebesma} \newline -->
<!-- \faIcon{phone} +49 251 83-33081 \newline -->
<!-- \faIcon{at} edzer.pebesma@uni-muenster.de \newline -->
<!-- \faIcon{envelope} Institute for Geoinformatics \newline -->
<!-- Heisenbergstraße 2, \newline -->
<!-- 48149 Münster, Germany -->

<!-- \textbf{Prof. Dr. Marco Painho} \newline -->
<!-- \faIcon{phone} +351 213 871 573 \newline -->
<!-- \faIcon{at} painho@novaims.unl.pt \newline -->
<!-- \faIcon{envelope} NOVA Information Management School \newline -->
<!-- Campus de Campolide\newline -->
<!-- 1070-312 Lisbon, Portugal -->

<!-- \textbf{Mag. Daniel Hölbling} \newline -->
<!-- \faIcon{phone} +43 (0)662 8044 7581 \newline -->
<!-- \faIcon{at} daniel.hoelbling@plus.ac.at \newline -->
<!-- \faIcon{envelope} Department of Geoinformatics - Z\_GIS 'newline -->
<!-- Schillerstrasse 30 \newline -->
<!-- 5020 Salzburg, Austria -->
<!-- \end{center} -->
<!-- \end{multicols} -->

<!-- \normalsize -->
